\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-20 chapters/1_intro.tex
Update figs; add extended CS results

\begin{figure}[t]
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=\textwidth]{./figs/intro_image.pdf} % left bottom right top
\caption{
 (\textbf{a}) Iterations of three different algorithms in the generalized framework on  toy graph examples with attractive (green) and repulsive (red) interactions. (\textbf{b}) Example of CREMI 2016 neuron-segmentation data \cite{cremiChallenge} overlaid with instance segmentation. (\textbf{c}) Agglomeration order, representing which pairs of neighboring pixels were merged first (white), later on (brown), or never (black).
 \TODO{re-arrange, show affinities and replace unsigned case with Abs Max}
%We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 
% On the left: a single cluster is returned with only attractive interactions.
 % main ideas and contributions
\label{fig:intro_figure}}
\end{figure}

>>>>

\begin{figure}[t]
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=0.9\textwidth]{./figs/intro_image_v2.pdf} % left bottom right top
\caption{ \textbf{Left:} raw data from the CREMI 2016 neuron-segmentation challenge and short- / long-range predictions of a CNN. \textbf{Right:} Outputs of three different agglomerative algorithms included in the proposed generalized framework. The  agglomeration order in (a) shows which pairs of neighboring pixels were merged first (white), later on (brown), or never (black). When signed graphs are used, the final clustering / instance segmentation is shown in (b). We also illustrate some iterations of the algorithms on toy graph examples with attractive (green) and repulsive (red) interactions.
%We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 
% On the left: a single cluster is returned with only attractive interactions.
 % main ideas and contributions
\label{fig:intro_figure}}
\end{figure}

### 2019-05-20 chapters/2_rel_work.tex
Finish polishing intro, abstract, conclusions
Update figs; add extended CS results

\textbf{Proposal-free methods} adopt a bottom-up approach by directly grouping pixels into instances. For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for instance segmentation; SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
% encode instance relationships to classes and exploit the boundary information  \cite{jin2016object}; 
a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction, whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic,kulikov2018instance}. % Semi-convolutiona: \cite{novotny2018semi}
% \TODO{What about \cite{liang2018proposal} using spectral clustering?}. 
Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrentPix}.
%  and introducing a ﬁxed number of labels (colors) and then dynamically assigning object instances to those labels during training (coloring) \cite{kulikov2018instance}

@@

\textbf{Clustering of signed graphs} has the goal of partitioning a graph with both attractive and repulsive cues. Finding an optimally balanced partitioning has a long history in combinatorial optimization \cite{grotschel1989cutting,grotschel1990facets,chopra1993partition}. %and can be done without the need to specify a termination criterion. 
NP-hardness of the \emph{correlation clustering} problem was shown in \cite{bansal2004correlation}, while the connection with graph multicuts was made by \cite{demaine2006correlation}. Modern integer linear programming solvers can tackle problems of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy agglomerative algorithms \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger graphs.
% \TODO{Cannot-link constraints?}
% Missing: Funke proposals, discussion about cannot-link constraints!!!

>>>>

\textbf{Proposal-free methods} adopt a bottom-up approach by directly grouping pixels into instances. Recently, there has been a growing interest for such  methods that do not involve object detection, since, in certain types of data, object instances cannot be approximated by bounding boxes. For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for instance segmentation; SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
% encode instance relationships to classes and exploit the boundary information  \cite{jin2016object}; 
a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction, whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic,kulikov2018instance}. % Semi-convolutiona: \cite{novotny2018semi}
% \TODO{What about \cite{liang2018proposal} using spectral clustering?}. 
Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrentPix}.
%  and introducing a ﬁxed number of labels (colors) and then dynamically assigning object instances to those labels during training (coloring) \cite{kulikov2018instance}

@@

\textbf{Clustering of signed graphs} has the goal of partitioning a graph with both attractive and repulsive cues. Finding an optimally balanced partitioning has a long history in combinatorial optimization \cite{grotschel1989cutting,grotschel1990facets,chopra1993partition}. %and can be done without the need to specify a termination criterion. 
NP-hardness of the \emph{correlation clustering} problem was shown in \cite{bansal2004correlation}, while the connection with graph multicuts was made by \cite{demaine2006correlation}. Modern integer linear programming solvers can tackle problems of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy agglomerative algorithms \cite{levinkov2017comparative,wolf2019mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger graphs.
% \TODO{Cannot-link constraints?}
% Missing: Funke proposals, discussion about cannot-link constraints!!!

### 2019-05-20 chapters/3_algorithm.tex
Update figs; add extended CS results

We consider an undirected simple edge-weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. In computer vision applications, the nodes can represent either pixels, superpixels or voxels. We call the set $\Pi$ a \emph{clustering} or \emph{partitioning} with $K$ clusters if $V = \cup_{S\in\Pi} S $, $\,S \cap \tilde{S} = \emptyset$ for different clusters $S, \tilde{S}\in \Pi$ and every cluster $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$. We also denote as $S_u$ the cluster associated with node $u$.
% \begin{equation}
% S_u \equiv S \in \Pi \,\, \text{s.t.} \,\, u \in S
% \end{equation}
% In this work, we consider the problem of clustering a weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. 
The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates to every edge a positive scalar attribute $w_e^+\in \mathbb{R}^+$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that other formalisms \UPDATE{REFS} for positively weighted graphs associate distances to the edges, thus, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+$.}. On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates to each edge a split tendency $w_e^- \in \mathbb{R}^+$: the higher this weight, the more the incident vertices would like to be in different clusters. 
Graphs of the type $\mathcal{G}(V,E,w^+, w^-)$ are also often defined as \emph{signed graphs} $\mathcal{G}(V,E,\cost)$, featuring positive and negative edge weights $\cost_e\in \mathbb{R}$. Following the theoretical considerations in \cite{lange2018partial}, we define these signed weights as ${\cost_e = w_e^+ - w_e^-}$. Some approaches directly compute $\cost_e$, whereas others compute $w_e^+$ and $w_e^-$ separately.
In this formalism, graphs with purely attractive interactions are a special case of $\mathcal{G}(V,E,\cost)$ with $\cost_e \geq 0, \, \forall e \in E$.

\textbf{Inter-cluster interaction } We call two clusters $S_u,S_v$ \emph{adjacent} if there exists at least one edge ${e_{ts}\in E}$ connecting a node $t\in S_u$ to a node $s\in S_v$. In hierarchical agglomerative clustering, the interaction $\interact(S_u,S_v)$ between the two clusters is usually defined as a function $\interact{}:\Pi \times \Pi \rightarrow \mathbb{R}$, named \emph{linkage criterion}, depending on the weights of \emph{all} edges connecting clusters $S_u$ and $S_v$, i.e. $E_{uv}=(S_u \times S_v) \cap E$. 
All the linkage criteria tested in this article are listed and defined in Table \ref{tab:linkage-criteria}.
% For example, for a \emph{maximum} linkage criterion statistic (single-linkage), the inter-cluster interaction is given by:
% \begin{equation}\label{eq:max_linkage}
% \interact_{S_1,S_2} = \, \max_{e\in U(S_u,S_v)} \cost(e), \qquad \text{where}\quad E_{12} = \{ e_{uv} \in E | u \in S_1, \, v \in S_2 \}.
% \end{equation}
% Other common choices are \emph{minimum} (complete linkage) or \emph{average} (average linkage). %and \emph{sum}.

@@

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{The table lists the existing clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm \algname{}, given a linkage criteria, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e. $E_{uv}=(S_u \times S_v) \cap E$.}
    \label{tab:linkage-criteria}
\end{table*}
\begin{figure}
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=\textwidth]{./figs/comparison.pdf} % left bottom right top
\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data. Only the few \emph{wrongly} segmented regions are highlighted in colors. Note that the data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.  Red arrows point to wrongly split regions. Yellow arrows point out merge errors. Green arrows indicate challenging, but correctly segmented regions. The average linkage without cannot-link constraints achieved an almost error-free segmentation.
% Only the involved segments are colored.
 % main ideas and contributions
\label{fig:cremi_comparison}}
\end{figure}

@@

In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
 the algorithm performs a standard agglomerative hierarchical clustering by returning only a single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see left panel of Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}} and Table \ref{tab:linkage-criteria}, unsigned graphs).

>>>>

We consider an undirected simple edge-weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. In computer vision applications, the nodes can represent either pixels, superpixels or voxels. We call the set $\Pi$ a \emph{clustering} or \emph{partitioning} with $K$ clusters if $V = \cup_{S\in\Pi} S $, $\,S \cap S' = \emptyset$ for different clusters $S, S'\in \Pi$ and every cluster $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$. We also denote as $S_u$ the cluster associated with node $u$.
% \begin{equation}
% S_u \equiv S \in \Pi \,\, \text{s.t.} \,\, u \in S
% \end{equation}
% In this work, we consider the problem of clustering a weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. 
The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates to every edge a positive scalar attribute $w_e^+\in \mathbb{R}^+$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that other formalisms \UPDATE{REFS} for positively weighted graphs associate distances to the edges, thus, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+$.}. On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates to each edge a split tendency $w_e^- \in \mathbb{R}^+$: the higher this weight, the more the incident vertices would like to be in different clusters. 
Graphs of the type $\mathcal{G}(V,E,w^+, w^-)$ are also often defined as \emph{signed graphs} $\mathcal{G}(V,E,\cost)$, featuring positive and negative edge weights $\cost_e\in \mathbb{R}$. Following the theoretical considerations in \cite{lange2018partial}, we define these signed weights as ${\cost_e = w_e^+ - w_e^-}$. Some approaches directly compute $\cost_e$, whereas others compute $w_e^+$ and $w_e^-$ separately.
In this formalism, graphs with purely attractive interactions are a special case of $\mathcal{G}(V,E,\cost)$ with $\cost_e \geq 0, \, \forall e \in E$.

\textbf{Inter-cluster interaction } We call two clusters $S_u,S_v$ \emph{adjacent} if there exists at least one edge ${e_{ts}\in E}$ connecting a node $t\in S_u$ to a node $s\in S_v$. In hierarchical agglomerative clustering, the interaction $\interact(S_u,S_v)$ between the two clusters is usually defined as a function $\interact{}:\Pi \times \Pi \rightarrow \mathbb{R}$, named \emph{linkage criterion}, depending on the weights of \emph{all} edges connecting clusters $S_u$ and $S_v$, i.e. $(S_u \times S_v) \cap E$. 
All the linkage criteria tested in this article are listed and defined in Table \ref{tab:linkage-criteria}.
% For example, for a \emph{maximum} linkage criterion statistic (single-linkage), the inter-cluster interaction is given by:
% \begin{equation}\label{eq:max_linkage}
% \interact_{S_1,S_2} = \, \max_{e\in U(S_u,S_v)} \cost(e), \qquad \text{where}\quad E_{12} = \{ e_{uv} \in E | u \in S_1, \, v \in S_2 \}.
% \end{equation}
% Other common choices are \emph{minimum} (complete linkage) or \emph{average} (average linkage). %and \emph{sum}.

@@

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{The table lists the existing clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm \algname{}, given a linkage criteria, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e. $E_{uv}=(S_u \times S_v) \cap E$.}
    \label{tab:linkage-criteria}
\end{table*}
\begin{figure}
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=\textwidth]{./figs/comparison_new.pdf} % left bottom right top
\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data. The main \emph{wrongly} segmented regions are highlighted in warm colors. Note that the data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.  Red arrows point to wrongly split regions. Yellow arrows point out merge errors. The average linkage without cannot-link constraints achieved an almost error-free segmentation.
% Only the involved segments are colored.
 % main ideas and contributions
\label{fig:cremi_comparison}}
\end{figure}

@@

In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
 the algorithm performs a standard agglomerative hierarchical clustering by returning only a single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see \UPDATE{left panel} of Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}} and Table \ref{tab:linkage-criteria}, unsigned graphs).

### 2019-05-20 chapters/5_experiments_noise.tex
Update figs; add extended CS results

\begin{figure}[t]
        \centering
\begin{minipage}[t]{0.48\textwidth}
% \begin{table}
    \centering
    \scriptsize
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}[t]{l|l|c}
        % \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \makecell[l]{\algname{}\\ Linkage} & \makecell{Arand-Score \\(higher is better)} \\ \midrule 
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
DTWS + LMC & -& 0.903 $\pm$ 0.016 \\
DTWS + MC & -& 0.903 $\pm$ 0.017 \\
% DTWS + avgHC &-& \\
% DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
% DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
THRESH &-& 0.221  $\pm$ 0.067 \\ 
% DTWS + \algname{} & Average& \TODO{} \\
% DTWS  & -& 0.010 $\pm$ 0.003\\
        \end{tabular}
    \captionof{table}{Arand-Scores achieved by different post-processing methods on CREMI challenge training predictions}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[t]{0.48\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
         & \makecell{CREMI Score \\(lower is better)}  \\ \midrule
Our UNet + DTWS + LMC &  \textbf{0.221}\\
PNI-UNet & 0.228 \\
Our UNet + \algname{} Avg-Linkage & 0.241 \\
MALA-UNet + MC \cite{funke2018large} & 0.276 \\
CRUNet \cite{zeng2017deepem3d} & 0.566  \\
LFC \cite{parag2017anisotropic} & 0.616  \\
% Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
% PNI-UNet & 0.228 & 0.116 \\
% Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
% MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
% CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
% LFC \cite{parag2017anisotropic} & 0.616 & \\
        \end{tabular}
        \vspace*{1.5em}
    \captionof{table}{Current leaderboard of the CREMI challenge}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}
\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
\begin{figure}
\centering
    %     \begin{subfigure}[t]{0.49 \textwidth}
    %     \centering
    %     \includegraphics[width=\textwidth,trim=0.55in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_only_direct.pdf}

>>>>

\begin{figure}[t]
        \centering
\begin{minipage}[t]{0.48\textwidth}
% \begin{table}
    \centering
    \scriptsize
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}[t]{l|l|c}
        % \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \makecell[l]{\algname{}\\ Linkage} & \makecell{Rand-Score \\(higher is better)} \\ \midrule 
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
DTWS + LMC & -& 0.903 $\pm$ 0.016 \\
DTWS + MC & -& 0.903 $\pm$ 0.017 \\
% DTWS + avgHC &-& \\
% DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
% DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
THRESH &-& 0.221  $\pm$ 0.067 \\ 
% DTWS + \algname{} & Average& \TODO{} \\
% DTWS  & -& 0.010 $\pm$ 0.003\\
        \end{tabular}
    \captionof{table}{Rand-Scores achieved by different post-processing methods on CREMI challenge training predictions}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[t]{0.48\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
         & \makecell{CREMI Score \\(lower is better)}  \\ \midrule
Our UNet + DTWS + LMC &  \textbf{0.221}\\
PNI-UNet & 0.228 \\
Our UNet + \algname{} Avg-Linkage & 0.241 \\
MALA-UNet + MC \cite{funke2018large} & 0.276 \\
CRUNet \cite{zeng2017deepem3d} & 0.566  \\
LFC \cite{parag2017anisotropic} & 0.616  \\
% Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
% PNI-UNet & 0.228 & 0.116 \\
% Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
% MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
% CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
% LFC \cite{parag2017anisotropic} & 0.616 & \\
        \end{tabular}
        \vspace*{1.1em}
    \captionof{table}{Current leaderboard of the CREMI challenge}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}
\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
\begin{figure}
\centering
    %     \begin{subfigure}[t]{0.49 \textwidth}
    %     \centering
    %     \includegraphics[width=\textwidth,trim=0.55in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_only_direct.pdf}
